|

### 2024-08-10 doc/paper.qmd
em4

### Aggregate Measure of Earnings Management

@@

>>>>

### Aggregate Measure of Earnings Management
The aggregate earnings management score is a summary measure that captures the overall level of earnings management in each country. This measure is calculated by ranking countries on each of the four individual earnings management measures (EM1-EM4), where a higher rank indicates a greater degree of earnings management. The final aggregate score is the average of these ranks, providing a comprehensive view of a country’s earnings management practices.

To calculate this measure:
$$
\text{Aggregate Earnings Management Score}_{\text{country}} = \frac{\text{Rank}_{\text{EM1}} + \text{Rank}_{\text{EM2}} + \text{Rank}_{\text{EM3}} + \text{Rank}_{\text{EM4}}}{4}
$$

@@

The replicated results show significant regional differences in EM4 values, reflecting varying degrees of loss avoidance. Spain has the highest EM4 value, highlighting strong loss avoidance among European firms. Norway, with the lowest EM4 value, corresponds to the minimum value in the original paper, confirming less aggressive loss avoidance. High EM4 values in Asian countries like Indonesia (5.667) and India (6.000) further support the trend that European and Asian firms exhibit greater loss avoidance than their Anglo-American counterparts, such as the United States (1.912) and Canada (2.402), which have lower EM4 values. These results align with the original study's conclusions on regional loss avoidance behavior.
